|

### 2021-05-20 article/resubmission.Rmd
messy updates

The first column of the graph reports the results for lower chamber size.
In the first model, which correlates lower chamber size and expenditure per capita, we find a
standardised mean difference (SMD) of `r round(mod[[1]]$TE.random,3)` and a standard error of `r round(mod[[1]]$seTE.random,3)`
(studies = `r mod[[1]]$k`, 95\% CI = [`r round(mod[[1]]$lower.random,3)`; `r round(mod[[1]]$upper.random,3)`], $p$-value = `r round(mod[[1]]$pval.random,3)` , prediction interval
= [`r round(mod[[1]]$lower.predict,3)`; `r round(mod[[1]]$upper.predict,3)`]). Therefore, we cannot reject the null hypothesis that the
effect size is zero. The $I^2$ statistic, which quantifies the degree of
heterogeneity among studies, is equal to `r round(mod[[1]]$I2*100, 2)`\%. $I^2$ values above 75\%
indicate very high study heterogeneity [@higgins2019cochrane].

@@

In our restricted sample, larger lower house size also does not increase
government spending as a percentage of GDP (studies = `r mod[[5]]$k`, SMD = `r round(mod[[5]]$TE.random,3)`, SE =
`r round(mod[[5]]$seTE.random,3)`, 95\% CI = [`r round(mod[[5]]$lower.random,3)`; `r round(mod[[5]]$upper.random,3)`], $p$-value = `r round(mod[[5]]$pval.random,3)`, prediction interval =
[`r round(mod[[5]]$lower.predict,3)`; `r round(mod[[5]]$upper.predict,3)`], $I^2$ = `r round(mod[[5]]$I2*100, 2)`\%). We find a positive effect in our extended
sample and the coefficient is statistically significant at the 10\% level
(coefficients = `r mod[[8]]$k`, SMD = `r round(mod[[8]]$TE.random,3)`, SE = `r round(mod[[8]]$seTE.random,3)`, 95\% CI = [`r round(mod[[8]]$lower.random,3)`; `r round(mod[[8]]$upper.random,3)`], $p$-value =
`r round(mod[[8]]$pval.random,3)`, prediction interval = [`r round(mod[[8]]$lower.predict,3)`; `r round(mod[[8]]$upper.predict,3)`], $I^2$ = `r round(mod[[8]]$I2*100, 2)`\%). The 
result supports the "law of 1/$n$", but the evidence is moderate
as the prediction interval include zero.

Next, we present the meta-analyses using the logarithm of lower house
size, as the main explanatory variable. We start with the relationship between
this variable and the logarithm of expenditure per capita. The result is positive and
statistically significant at 10\%, but the prediction interval encompasses zero
(studies = `r mod[[4]]$k`, SMD = `r round(mod[[4]]$TE.random,3)`, SE = `r round(mod[[4]]$seTE.random,3)`, 95\% CI = [`r round(mod[[4]]$lower.random,3)`; `r round(mod[[4]]$upper.random,3)`], $p$-value =
`r round(mod[[4]]$pval.random,3)`, prediction interval = [`r round(mod[[4]]$lower.predict,3)`; `r round(mod[[4]]$upper.predict,3)`], $I^2$ = `r round(mod[[4]]$I2*100, 2)`\%). Although the
coefficient has the predicted sign, we should interpret the finding with caution
as it does not replicate in our sample of `r dim(fulldat)[1]` effect sizes.

@@

The third set of models uses upper house size, as the main independent
variable. We find a positive correlation between this variable and expenditure per capita
but the coefficient is not significant (studies = `r mod[[2]]$k`, SMD = `r round(mod[[2]]$TE.random,3)`, SE
= `r round(mod[[2]]$seTE.random,3)`, 95\% CI = [`r round(mod[[2]]$lower.random,3)`; `r round(mod[[2]]$upper.random,3)`], $p$-value = `r round(mod[[2]]$pval.random,3)`, prediction interval =
[`r round(mod[[2]]$lower.predict,3)`; `r round(mod[[2]]$upper.predict,3)`], $I^2$ = `r round(mod[[2]]$I2*100, 2)`\%). But as with the other models, the prediction
interval again includes zero. When we run the same analysis in the extended
sample, we see a significant coefficient for the estimate, yet the prediction interval also
contains zero (coefficients = `r mod[[9]]$k`, SMD = `r round(mod[[9]]$TE.random,3)`, SE = `r round(mod[[9]]$seTE.random,3)`, 95\% CI = [`r round(mod[[9]]$lower.random,3)`; `r round(mod[[9]]$upper.random,3)`],
$p$-value $<$ 0.001, prediction interval = [`r round(mod[[9]]$lower.predict,3)`; `r round(mod[[9]]$upper.predict,3)`], $I^2$ = `r round(mod[[9]]$I2*100, 2)`\%).

@@

In this section, we run a series of meta-regressions with covariates that may
account for differences across the selected papers. The first variable indicates
whether the study uses lower chamber size, log lower chamber size, or upper chamber size as a main explanatory variable. We included the individual effect sizes for upper and lower chamber sizes when papers analyzed both.
The second variable shows the study publication year, which we included to
capture temporal variation in the study coefficients. We also add a dummy
variable to assess whether published articles report effect sizes that are
higher or lower than those from working papers. The fourth variable measures
whether studies focusing on non-majoritarian electoral systems report
coefficients that are smaller or larger than those from majoritarian countries.
Our last covariate is a categorical variable indicating the statistical
procedure used in the original models (panel data, instrumental variables,
OLS, or regression discontinuity design).

@@

\footnotetext{\textbf{Note:} {The restricted and extended samples include `r length(dat$id)` and `r length(fulldat$id)` study coefficients, respectively. We report the results from the permutation tests. Reference categories: Independent Variable $= k$; Published $= Yes$; Non-Majoritarian (PR \& Mixed) $= Majoritarian$; Method $= OLS$. Significance codes: *** $p < 0.01$; ** $p < 0.05$; * $p < 0.10$.}}

@@

Table \ref{tabregressions} presents the meta-regression results for our
restricted and extended samples. Each column represents one of the three
measures of public spending we discuss in this paper. Each subgroup uses a chosen category as reference. When it comes to the independent variable, the reference category is upper chamber size; for 
publication bias, the reference is published articles; for electoral system, the reference is majoritarian systems; and for methodology, the reference is ordinary least squares linear regression. To reduce the risk of
false positives in our analyses, we use permutation tests to calculate
significance levels for the meta-regressions \citep{higgins2004controlling}.

>>>>

The first line of graphs reports the results for lower chamber size.
In the first model, which correlates lower chamber size and expenditure per capita, we find a
standardised mean difference (SMD) of `r round(mod[[1]]$TE.random,3)` and a standard error of `r round(mod[[1]]$seTE.random,3)`
(studies = `r mod[[1]]$k`, 95\% CI = [`r round(mod[[1]]$lower.random,3)`; `r round(mod[[1]]$upper.random,3)`], $p$-value = `r round(mod[[1]]$pval.random,3)` , prediction interval
= [`r round(mod[[1]]$lower.predict,3)`; `r round(mod[[1]]$upper.predict,3)`]). Therefore, we cannot reject the null hypothesis that the
effect size is zero. The $I^2$ statistic, which quantifies the degree of
heterogeneity among studies, is equal to `r round(mod[[1]]$I2*100, 2)`\%. $I^2$ values above 75\%
indicate very high study heterogeneity [@higgins2019cochrane].

@@

In our restricted sample, larger lower house size also does not increase
government spending as a percentage of GDP (studies = `r mod[[5]]$k`, SMD = `r round(mod[[5]]$TE.random,3)`, SE =
`r round(mod[[5]]$seTE.random,3)`, 95\% CI = [`r round(mod[[5]]$lower.random,3)`; `r round(mod[[5]]$upper.random,3)`], $p$-value = `r round(mod[[5]]$pval.random,3)`, prediction interval =
[`r round(mod[[5]]$lower.predict,3)`; `r round(mod[[5]]$upper.predict,3)`], $I^2$ = `r round(mod[[5]]$I2*100, 2)`\%). In the extended sample the effect is negative, but it is also statistically insignificant.

```{r}
#We find a positive effect in our extended
#sample and the coefficient is statistically significant at the 10\% level
#(coefficients = `r mod[[8]]$k`, SMD = `r round(mod[[8]]$TE.random,3)`, SE = `r round(mod[[8]]$seTE.random,3)`, 95\% CI = [`r round(mod[[8]]$lower.random,3)`; `r round(mod[[8]]$upper.random,3)`], $p$-value =
#`r round(mod[[8]]$pval.random,3)`, prediction interval = [`r round(mod[[8]]$lower.predict,3)`; #`r round(mod[[8]]$upper.predict,3)`], $I^2$ = `r round(mod[[8]]$I2*100, 2)`\%). The 
#result supports the "law of 1/$n$", but the evidence is moderate
#as the prediction interval include zero.
```

Next, we present the meta-analyses using the logarithm of lower house
size. We start with the relationship between
this variable and the logarithm of expenditure per capita. The result is positive, but the coefficient is not significant, and the prediction interval encompasses zero
(studies = `r mod[[4]]$k`, SMD = `r round(mod[[4]]$TE.random,3)`, SE = `r round(mod[[4]]$seTE.random,3)`, 95\% CI = [`r round(mod[[4]]$lower.random,3)`; `r round(mod[[4]]$upper.random,3)`], $p$-value =
`r round(mod[[4]]$pval.random,3)`, prediction interval = [`r round(mod[[4]]$lower.predict,3)`; `r round(mod[[4]]$upper.predict,3)`], $I^2$ = `r round(mod[[4]]$I2*100, 2)`\%). Results in the full sample are also null.

@@

The third set of models uses upper house size as the main independent
variable. We find a positive correlation between this variable and expenditure per capita
but the coefficient is not significant (studies = `r mod[[2]]$k`, SMD = `r round(mod[[2]]$TE.random,3)`, SE
= `r round(mod[[2]]$seTE.random,3)`, 95\% CI = [`r round(mod[[2]]$lower.random,3)`; `r round(mod[[2]]$upper.random,3)`], $p$-value = `r round(mod[[2]]$pval.random,3)`, prediction interval =
[`r round(mod[[2]]$lower.predict,3)`; `r round(mod[[2]]$upper.predict,3)`], $I^2$ = `r round(mod[[2]]$I2*100, 2)`\%). But as with the other models, the prediction
interval again includes zero. When we run the same analysis in the extended
sample, we see a significant coefficient for the estimate, yet the prediction interval also
contains zero (coefficients = `r mod[[9]]$k`, SMD = `r round(mod[[9]]$TE.random,3)`, SE = `r round(mod[[9]]$seTE.random,3)`, 95\% CI = [`r round(mod[[9]]$lower.random,3)`; `r round(mod[[9]]$upper.random,3)`],
$p$-value $<$ 0.001, prediction interval = [`r round(mod[[9]]$lower.predict,3)`; `r round(mod[[9]]$upper.predict,3)`], $I^2$ = `r round(mod[[9]]$I2*100, 2)`\%).

@@

In this section, we run a series of meta-regressions with covariates that may
account for differences across the selected papers. The first variable indicates
whether the study uses lower chamber size, log lower chamber size, or upper chamber size as a main explanatory variable. We included the individual effect sizes for upper and lower chamber sizes when papers analyzed both.
The second variable shows the study publication year, which we included to
capture temporal variation in the study coefficients. We also add a dummy
variable to assess whether published articles report effect sizes that are
higher or lower than those from working papers. The fourth variable measures
whether studies focusing on non-majoritarian electoral systems report
coefficients that are smaller or larger than those from majoritarian countries. The fifth covariate is a categorical variable indicating the statistical
procedure used in the original models (panel data, instrumental variables,
OLS, or regression discontinuity design). In our last variable, we separate coefficients that use samples from unicameral or bicameral systems, and code papers using polities with different institutional designs as "mixed".

@@

\footnotetext{\textbf{Note:} {The restricted and extended samples include `r length(dat$id)` and `r length(fulldat$id)` study coefficients, respectively. We report the results from the permutation tests. Reference categories: Independent Variable $= k$; Published $= Yes$; Non-Majoritarian (PR \& Mixed) $= Majoritarian$; Method $= OLS$; Institutional Design $= Bicameralism$. Significance codes: *** $p < 0.01$; ** $p < 0.05$; * $p < 0.10$.}}

@@

Table \ref{tabregressions} presents the meta-regression results for our
restricted and extended samples. Each column represents one of the three
measures of public spending we discuss in this paper. To reduce the risk of
false positives in our analyses, we use permutation tests to calculate
significance levels for the meta-regressions \citep{higgins2004controlling}.
